### 2014-11-13 tex/abstract.tex
Changed one letter

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated
data. Generalized symbolic execution (GSE) techniques have addressed
this challenge by materializing a concrete heap lazily during field
accesses.  This approach however, exacerbates the state space
explosion problem.  In this work, we present a novel symbolic
execution technique which takes inspiration from the static analysis
domain and defines a novel bipartite graph representation of the heap
and a lazy initialization algorithm that, unlike state-of-the-art
techniques, (a) supports aliasing, (b) does not require rewrite of
constraints on heap updates, (c) can initialize the heap-on-the-fly,
and (d) reduces the number of points of non-determinism during the
search. Our approach is sound and complete with respect to the
properties provable by GSE. A preliminary evaluation of our
implementation in Java Pathfinder shows the summary heap enables the
initialization of larger, more complex heaps than previously possible.

>>>>

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated
data. Generalized symbolic execution (GSE) techniques have addressed
this challenge by materializing a concrete heap lazily during field
accesses.  This approach however, exacerbates the state space
explosion problem.  In this work, we present a novel symbolic
execution technique which takes inspiration from the static analysis
domain and defines a novel bipartite graph representation of the heap
and a lazy initialization algorithm that, unlike state-of-the-art
techniques, (i) supports aliasing, (ii) does not require rewrite of
constraints on heap updates, (iii) can initialize the heap-on-the-fly,
and (iv) reduce the number of points of non-determinism during the
search. Our approach is sound and complete with respect to the
properties provable by GSE. A preliminary evaluation of our
implementation in Java Pathfinder shows the summary heap enables the
initialization of larger, more complex heaps than previously possible.
